Manuscript

### 2023-05-23 Manuscript.Rmd
updates

mu_sigmaEta = seq(0.1,1,length.out = 3)
mu_sigmaPsi = seq(0.1,1,length.out = 3)
mu_sigmaEpsilon = seq(0.1,1,length.out = 3)

sd_sigmaEta = seq(0.1,1,length.out = 3)
sd_sigmaPsi = seq(0.1,1,length.out = 3)
sd_sigmaEpsilon = seq(0.1,1,length.out = 3)

@@

@@

df = df %>% filter(session == 1, id > 40)

@@

mod = cmdstan_model(here::here("Stan","myKalmanfilter_v2.stan"))

@@

mod = cmdstan_model(here::here("Stan","myKalmanfilter_v2.stan"))

kalman_fit_sess1 <- mod$sample(
      data = data1,
      chains = 4,
      parallel_chains = 4,
      refresh = 100,
      adapt_delta = 0.90,
      max_treedepth = 12
    )
```

>>>>

mu_sigmaEta = seq(0.1,1,length.out = 3)
mu_sigmaPsi = seq(0.1,5,length.out = 3)
mu_sigmaEpsilon = seq(0.1,5,length.out = 3)

sd_sigmaEta = seq(0.1,1,length.out = 2)
sd_sigmaPsi = seq(0.1,1,length.out = 2)
sd_sigmaEpsilon = seq(0.1,1,length.out = 2)

sd_precision_percept = seq(0.1,1, length.out = 2)

sd_beta = seq(0.1,1, length.out = 2)

@@

#plan(multisession, workers = availableCores()-1)

data_list = data_list[1:2]

@@

@@

mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))

@@

mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))

kalman_fit_sess2 <- mod$sample(
      data = data1,
      chains = 4,
      parallel_chains = 4,
      refresh = 100,
      adapt_delta = 0.90,
      max_treedepth = 12
    )
```
